---
title: "Biostat 203B Homework 4"
subtitle: Due Mar 24 @ 11:59PM
author: Zoe and 106070449
format:
  html:
    theme: cosmo
    embed-resources: true
    number-sections: true
    toc: true
    toc-depth: 4
    toc-location: left
    code-fold: false
knitr:
  opts_chunk: 
    cache: false    
    echo: true
    fig.align: 'center'
    fig.width: 6
    fig.height: 4
    message: FALSE
---

Display machine information:

```{r}
sessionInfo()
```

Load database libraries and the tidyverse frontend:

```{r}
#| eval: false
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(tidymodels))
suppressPackageStartupMessages(library(lubridate))
```

## Predicting 30-day mortality

Using the ICU cohort `icu_cohort.rds` you built in Homework 3, develop at least three analytic approaches for predicting the 30-day mortality of patients admitted to ICU using demographic information (gender, age, marital status, ethnicity), first lab measurements during ICU stay, and first vital measurements during ICU stay. For example, you can use (1) logistic regression with elastic net (lasso + ridge) penalty (e.g., glmnet or keras package), (2) random forest, (3) boosting, and (4) support vector machines, or (5) MLP neural network (keras package)

1.  Partition data into 50% training set and 50% test set. Stratify partitioning according the 30-day mortality status.

2.  Train and tune the models using the training set.

3.  Compare model classification performance on the test set. Report both the area under ROC curve and accuracy for each model.

load necessary library

```{r}
library(GGally)
library(gtsummary)
library(ranger)
library(glmnet)
library(xgboost)
```

import the dataset

**Data Cleaning :**  I only keep some of the intersting variables in the final 
dataset before we split into test and train datasets. 
```{r}
icu_cohort <-read_rds("icu_cohort.rds") %>%
  # first column is patient ID, which we don't need
  select(day30mort, marital_status, ethnicity, gender, 
         #start of the quantitative variables
  Sodium, Glucose, Chloride, Potassium, Creatinine, Hematocrit, Bicarbonate, 
  White_Blood_Cells, Temperature_Fahrenheit, 
  Non_Invasive_Blood_Pressure_systolic, 
  Non_Invasive_Blood_Pressure_mean, 
  Respiratory_Rate, 
  Heart_Rate, 
  age_at_admission) %>%
  
  print(width = Inf)

```


We are here to deal with the unusual Fahrenheit in the degrees.
All degrees between 45 and 90 will be considered typo and switch to NA since 
normal humans won't have deegress in this range no matter it is C or F.
Temperature lower than 32 will also be deleted since it is also not a human
temperature.  Temperature beetween 34 to 45 will be converted into Fahrenheit. 

```{r}
icu_cohort$Temperature_Fahrenheit[icu_cohort$Temperature_Fahrenheit <= 34 
                            & !is.na(icu_cohort$Temperature_Fahrenheit)] <- NA
icu_cohort$Temperature_Fahrenheit[icu_cohort$Temperature_Fahrenheit > 45 
                                & icu_cohort$Temperature_Fahrenheit < 90 
                            & !is.na(icu_cohort$Temperature_Fahrenheit)] <- NA
icu_cohort$Temperature_Fahrenheit[icu_cohort$Temperature_Fahrenheit > 34 
                                & icu_cohort$Temperature_Fahrenheit <= 45 & 
                                 !is.na(icu_cohort$Temperature_Fahrenheit)] <- 
icu_cohort$Temperature_Fahrenheit * 9 / 5 + 32
icu_cohort$Temperature_Fahrenheit[icu_cohort$Temperature_Fahrenheit >= 115 
                            & !is.na(icu_cohort$Temperature_Fahrenheit)] <- NA
```



Change the 'UNKNOWN' in ethnicity into NA
```{r}
icu_cohort$ethnicity[icu_cohort$ethnicity == 'UNKNOWN'] <- NA
icu_cohort$day30mort = as.factor(icu_cohort$day30mort)   
```

```{r}
icu_cohort %>% tbl_summary(by = day30mort)
```




find the columns with missing values for later process

```{r}
names(which(colSums(is.na(icu_cohort)) > 0))
```

split the data for the rceipt, we use median for quantitative data and mode for 
qualitative data. 
Based on the resulf of the table, none of these variables have a lot of NA
so we don't need to we further eliminate some variables that have many unknowns.

#1 Linear regresion
```{r}
set.seed(203)

data_split <- initial_split(
  icu_cohort,
  # stratify by AHD
  strata = "day30mort", 
  prop = 0.5
  )
data_split

ICU_other <- training(data_split)
dim(ICU_other)

ICU_test <- testing(data_split)
dim(ICU_test)
```


create the Recipe for ogistic reegression

```{r}
logit_recipe <- 
  recipe(
    day30mort ~ ., 
    data = ICU_other
  ) %>%
  # mean and mode imputation 
  step_impute_mode( marital_status, ethnicity) %>%
  step_impute_mean("Sodium", "Glucose", "Chloride", "Potassium", "Creatinine", 
 "Hematocrit", "Bicarbonate", "White_Blood_Cells", "Temperature_Fahrenheit", 
 "Non_Invasive_Blood_Pressure_systolic", "Non_Invasive_Blood_Pressure_mean", 
 "Respiratory_Rate", "Heart_Rate" ) %>%
  # create traditional dummy variables
  step_dummy(all_nominal_predictors()) %>%
  # zero-variance filter
  step_zv(all_numeric_predictors()) %>% 
  # center and scale numeric data
  step_normalize(all_numeric_predictors()) %>%
  # estimate the means and standard deviations
  prep(training = ICU_other, retain = TRUE)
logit_recipe
```

create the model

```{r}
logit_mod <- 
  logistic_reg(
    penalty = tune(), 
    mixture = tune()
  ) %>% 
  set_engine("glmnet", standardize = FALSE)
logit_mod
```

```{r}
logit_wf <- workflow() %>%
  add_recipe(logit_recipe) %>%
  add_model(logit_mod)
logit_wf
```


```{r}
param_grid <- grid_regular(
  penalty(range = c(-6, 3)), 
  mixture(),
  levels = c(100, 5)
  )
param_grid
```

```{r}
set.seed(203)

folds <- vfold_cv(ICU_other, v = 5)
folds
```
Fit cross-validation.
```{r}
logit_fit <- logit_wf %>%
  tune_grid(
    resamples = folds,
    grid = param_grid,
    metrics = metric_set(roc_auc, accuracy)
    )
logit_fit
```

```{r}
logit_fit %>%
  collect_metrics() %>%
  print(width = Inf) %>%
  filter(.metric == "roc_auc") %>%
  ggplot(mapping = aes(x = penalty, y = mean, color = mixture)) +
  geom_point() +
  labs(x = "Penalty", y = "CV AUC") +
scale_x_log10()
```
```{r}
logit_fit %>%
  show_best("roc_auc")
```

```{r}
best_logit <- logit_fit %>%
  select_best("roc_auc")
best_logit
```

```{r}
final_wf <- logit_wf %>%
  finalize_workflow(best_logit)
final_wf
```

```{r}
final_fit <- 
  final_wf %>%
  last_fit(data_split)
final_fit
```

```{r}
final_fit %>% 
  collect_metrics()
```

#2. Random Forest
```{r}
rf_recipe <- 
  recipe(
    day30mort ~ ., 
    data = ICU_other
  ) %>%
  # mean and mode imputation 
  step_impute_mode( marital_status, ethnicity) %>%
  step_impute_mean("Sodium", "Glucose", "Chloride", "Potassium", "Creatinine", 
 "Hematocrit", "Bicarbonate", "White_Blood_Cells", "Temperature_Fahrenheit", 
 "Non_Invasive_Blood_Pressure_systolic", "Non_Invasive_Blood_Pressure_mean", 
 "Respiratory_Rate", "Heart_Rate" ) %>%
  # create traditional dummy variables
  step_dummy(all_nominal_predictors()) %>%
  # zero-variance filter
  step_zv(all_numeric_predictors()) %>% 
  # center and scale numeric data
  #step_normalize(all_numeric_predictors()) %>%
  # estimate the means and standard deviations
  prep(training = ICU_other, retain = TRUE)
rf_recipe
```

```{r}
rf_mod <- 
  rand_forest(
    mode = "classification",
    # Number of predictors randomly sampled in each split
    mtry = tune(),
    # Number of trees in ensemble
    trees = tune()
  ) %>% 
  set_engine("ranger")
rf_mod
```

```{r}
rf_wf <- workflow() %>%
  add_recipe(rf_recipe) %>%
  add_model(rf_mod)
rf_wf
```
```{r}
param_grid <- grid_regular(
  trees(range = c(100L, 300L)), 
  mtry(range = c(1L, 5L)),
  levels = c(3, 5)
  )
param_grid
```
```{r}
set.seed(203)

folds <- vfold_cv(ICU_other, v = 5)
folds
```

```{r}
rf_fit <- rf_wf %>%
  tune_grid(
    resamples = folds,
    grid = param_grid,
    metrics = metric_set(roc_auc, accuracy)
    )
rf_fit
```
```{r}
rf_fit %>%
  collect_metrics() %>%
  print(width = Inf) %>%
  filter(.metric == "roc_auc") %>%
  ggplot(mapping = aes(x = trees, y = mean, color = mtry)) +
  geom_point() + 
  # geom_line() + 
  labs(x = "Num. of Trees", y = "CV AUC")
```
Show the top 5 models.
```{r}
rf_fit %>%
  show_best("roc_auc")
```

Let’s select the best model.
```{r}
best_rf <- rf_fit %>%
  select_best("roc_auc")
best_rf
```

```{r}
# Final workflow
final_wf <- rf_wf %>%
  finalize_workflow(best_rf)
final_wf
```
```{r}
# Fit the whole training set, then predict the test cases
final_fit <- 
  final_wf %>%
  last_fit(data_split)
final_fit
```

```{r}
# Test metrics
final_fit %>% 
  collect_metrics()
```

#3 XGBooST


Create recipe for the xgboost
```{r}
gb_recipe <- 
  recipe(
    day30mort ~ ., 
    data = ICU_other
  ) %>%
  # mean and mode imputation 
  step_impute_mode( marital_status, ethnicity) %>%
  step_impute_mean("Sodium", "Glucose", "Chloride", "Potassium", "Creatinine", 
 "Hematocrit", "Bicarbonate", "White_Blood_Cells", "Temperature_Fahrenheit", 
 "Non_Invasive_Blood_Pressure_systolic", "Non_Invasive_Blood_Pressure_mean", 
 "Respiratory_Rate", "Heart_Rate" ) %>%
  # create traditional dummy variables
  step_dummy(all_nominal_predictors()) %>%
  # zero-variance filter
  step_zv(all_numeric_predictors()) %>% 
  # center and scale numeric data
  #step_normalize(all_numeric_predictors()) %>%
  # estimate the means and standard deviations
  prep(training = ICU_other, retain = TRUE)
gb_recipe
```
```{r}
gb_mod <- 
  boost_tree(
    mode = "classification",
    trees = 1000, 
    tree_depth = tune(),
    learn_rate = tune()
  ) %>% 
  set_engine("xgboost")
gb_mod
```

```{r}
gb_wf <- workflow() %>%
  add_recipe(gb_recipe) %>%
  add_model(gb_mod)
gb_wf
```

```{r}
param_grid <- grid_regular(
  tree_depth(range = c(1L, 3L)),
  learn_rate(range = c(-5, 2), trans = log10_trans()),
  levels = c(3, 10)
  )
param_grid
```
Set cross-validation partitions.

```{r}
set.seed(203)

folds <- vfold_cv(ICU_other, v = 5)
folds
```

```{r}
gb_fit <- gb_wf %>%
  tune_grid(
    resamples = folds,
    grid = param_grid,
    metrics = metric_set(roc_auc, accuracy)
    )
gb_fit
```

Visualize CV results:
```{r}
gb_fit %>%
  collect_metrics() %>%
  print(width = Inf) %>%
  filter(.metric == "roc_auc") %>%
  ggplot(mapping = aes(x = learn_rate, y = mean, color = tree_depth)) +
  geom_point() +
  labs(x = "Learning Rate", y = "CV AUC") +
  scale_x_log10()
```
```{r}
gb_fit %>%
  show_best("roc_auc")
```

```{r}
best_gb <- gb_fit %>%
  select_best("roc_auc")
best_gb
```

```{r}
# Final workflow
final_wf <- gb_wf %>%
  finalize_workflow(best_gb)
final_wf
```
```{r}
final_fit <- 
  final_wf %>%
  last_fit(data_split)
final_fit
```

```{r}
final_fit %>% 
  collect_metrics()
```

