---
title: "Biostat 203B Homework 3"
subtitle: Due Mar 1 @ 11:59PM
author: Zoe (Yijin) Zhao and UID 106070449
format:
  html:
    theme: cosmo
    number-sections: true
    toc: true
    toc-depth: 4
    toc-location: left
    code-fold: false
knitr:
  opts_chunk: 
    cache: false    
    echo: true
    fig.align: 'center'
    fig.width: 6
    fig.height: 4
    message: FALSE
---

Display machine information:
```{r}
sessionInfo()
```

Load database libraries and the tidyverse frontend:
```{r}
library(bigrquery)
library(dbplyr)
library(DBI)
library(lubridate)
library(tidyverse)
```

I found the current versions of bigrquery (v1.4.1) and dbplyr (v2.3.0) don't work well together on my computer ([Issue](https://github.com/r-dbi/bigrquery/issues/509)). If you encounter similar issues, you can install older versions of the these two packages.
```{r}
#| eval: false
library(devtools)
install_version("bigrquery", version = "1.4.0")
install_version("dbplyr", version = "2.1.1")
```

## Q1. Compile the ICU cohort in HW2 from the Google BigQuery database 

Below is an outline of steps.

1. Load the GCP BigQuery service account token. Please place the service account token (available at BruinLearn) at your MIMIC data folder: `~/mimic/biostat-203b-2022winter-3fdc2392ac39.json`.
```{r}
# path to the service account token 
satoken <- "~/mimic/biostat-203b-2023winter-3fdc2392ac39.json"
# BigQuery authentication using service account
bq_auth(
  path = satoken,
   email = "mimiciv-bigquery@biostat-203b-2023winter.iam.gserviceaccount.com",
   scopes = c("https://www.googleapis.com/auth/bigquery",
     "https://www.googleapis.com/auth/cloud-platform")
)
```

1. Connect to BigQuery database `mimic4_v1_0_203b` in GCP (Google Cloud Platform), using the billing account `biostat-203b-2022winter`.
```{r}
# Connect to the BigQuery database `biostat-203b-2022winter.mimic4_v1_0_203b`
con <- dbConnect(
    bigrquery::bigquery(), 
    project = "biostat-203b-2022winter", 
    dataset = "mimic4_v1_0_203b", 
    billing = "biostat-203b-2022winter"
)
con
```

**Solution: ** Done

2. List all tables in the `mimic4_v1_0_203b` database.
```{r}
dbListTables(con)
```
**Solution: ** Done

3. Connect to the `icustays` table.
```{r}
# full ICU stays table
icustays_tble <- tbl(con, "icustays") %>%
  show_query() %>%
  print(width = Inf)
```
We only keep the first ICU stay. Following code is kind of a hack, using the `summarise_all(min)` function. It seems that `slice_min()`, `slice_head()`, `distinct(, .keep_all = TRUE)` don't work with `dbplyr`+`bigrquery` at the moment.
```{r}
icustays_tble <- icustays_tble %>% 
  select(subject_id, intime) %>% 
  group_by(subject_id) %>% 
  summarise_all(min) %>%
  left_join(icustays_tble, by = c("subject_id", "intime")) %>%
  show_query() %>%
  print(width = Inf)
```


4. Connect to the `admissions` table and only keep the patients who have a match in `icustays_tble` (according to `subject_id` and `hadm_id`).
```{r}
admissions_tble <- tbl(con, "admissions") %>%
  semi_join(icustays_tble, by = c("subject_id", "hadm_id")) %>%
  show_query() %>%
  print(width = Inf)
```

5. Connect to the `patients` table and only keep the patients who have a match in `icustays_tble` (according to `subject_id`).
```{r}
patients_tble <- tbl(con, "patients") %>%
  semi_join(icustays_tble, by = c("subject_id")) %>%
  show_query() %>%
  print(width = Inf)
```

6. Connect to the `labevents` table and retrieve a subset that only contain subjects who appear in `icustays_tble` and the lab items listed in HW2. 
```{r}
itemid_want <- c(50912, 50971, 50983, 50902, 50882, 51221, 51301, 50931)
labevents_tble <- tbl(con, "labevents") %>%
  filter(itemid %in% itemid_want) %>%
  semi_join(icustays_tble, by = c("subject_id")) %>%
  show_query() %>%
  print(width = Inf)
```

```{r}
d_labitems_tble <- tbl(con, 'd_labitems') %>%
  filter(itemid %in% itemid_want) %>%
  mutate(label = str_replace(label, '\\s', '_')) %>%
  show_query() %>%
  print(width = Inf)
```


Only keep the first lab measurements during ICU stay and pivot lab items to become variables/columns.
```{r}
labevents_tble <- labevents_tble %>%
  select(subject_id, itemid, valuenum, charttime) %>%
  left_join(select(icustays_tble, subject_id, intime, outtime),
     by = c("subject_id")) %>%
  filter(charttime >= intime & charttime <= outtime) %>%
  # Keep the first measurement of each lab item for each patient
  select(subject_id, itemid, charttime) %>%
  group_by(subject_id, itemid) %>%
  summarise_all(min) %>%
  left_join(labevents_tble, by = 
              c("subject_id", "itemid", "charttime")) %>%
   #attach label for each itemid so we could pivot with label
  left_join(select(d_labitems_tble, label, itemid), by = c('itemid')) %>%
   #important to take off before pivot wider or multiple rows for itemid
  select(subject_id, label, valuenum) %>% 
  pivot_wider(names_from = label, values_from = valuenum) %>%
  show_query() %>%
  print(width = Inf)
```

7. Connect to `chartevents` table and retrieve a subset that only contain subjects who appear in `icustays_tble` and the chart events listed in HW2.
```{r}
ditemid_want <- c(220045, 220181, 220179, 223761, 220210)
chartevents_tble <- tbl(con, "chartevents") %>%
  filter(itemid %in% ditemid_want) %>%
  semi_join(icustays_tble, by = c("subject_id")) %>%
  show_query() %>%
  print(width = Inf)
```

```{r}
d_items_tble <- tbl(con, 'd_items') %>%
  filter(itemid %in% ditemid_want) %>%
  mutate(label = str_replace(label, '\\s', '_')) %>%
  show_query() %>%
  print(width = Inf)
```

Only keep the first chart events during ICU stay and pivot chart events to become variables/columns.
```{r}
chartevents_tble <- chartevents_tble %>%
  left_join(select(icustays_tble, subject_id, intime, outtime),
     by = c("subject_id")) %>%
  filter(charttime >= intime & charttime <= outtime) %>%
  # Keep the first measurement of each lab item for each patient
  select(subject_id, itemid, charttime) %>%
  group_by(subject_id, itemid) %>%
  summarise_all(min) %>%
  left_join(chartevents_tble, by = 
              c("subject_id", "charttime", 'itemid')) %>%
   #attach label for each itemid so we could pivot with label
  left_join(select(d_items_tble, label, itemid), by = c('itemid')) %>%
   #important to take off before pivot wider or multiple rows for itemid
  select(subject_id, label, valuenum) %>% 
  pivot_wider(names_from = label, values_from = valuenum) %>%
  show_query() %>%
  print(width = Inf)
```

8. Put things together. This step is similar to Q7 of HW2. Using one chain of pipes `%>%` to perform following data wrangling steps: (i) start with the `icustays_tble` for the first ICU stay of each unique patient, (ii) merge in admissions and patients tables, (iii) keep adults only (age at admission >= 18), (iv) merge in the labevents and chartevents tables, (v) create an indicator for 30-day mortality, (vi) save the final tibble to an `icu_cohort.rds` R data file in the `mimiciv_shiny` folder.

```{r}
# make a directory mimiciv_shiny
if (!dir.exists("mimiciv_shiny")) {
  dir.create("mimiciv_shiny")
}
```

```{r}
icu_cohort <- icustays_tble %>%
  #join all variables
  left_join(admissions_tble, by = c("subject_id", "hadm_id")) %>%
  left_join(patients_tble, by = c("subject_id")) %>%
  left_join(labevents_tble, by = c("subject_id")) %>%
  left_join(chartevents_tble, by = c("subject_id")) %>%
  #get the age of the patents
  mutate(age_at_admission =  year(admittime) - anchor_year + anchor_age) %>%
  filter(age_at_admission >= 18) %>%
  mutate(day30mort = 
           ifelse(is.na(deathtime), FALSE,
           DATE_DIFF(date(deathtime), date(admittime), DAY) <= 30)) %>%
  # (vi) save the final tibble to an `icu_cohort.rds` in `mimiciv_shiny`
  collect() %>%
  write_rds("mimiciv_shiny/icu_cohort.rds") %>%
  # show_query() %>%
  print(width = Inf)
```

Close database connection and clear workspace.
```{r, eval=F}
dbDisconnect(con)
rm(list = ls())
```

## Q2. Shiny app

Develop a Shiny app for exploring the ICU cohort data created in Q1. The app should reside in the `mimiciv_shiny` folder. The app should provide easy access to the graphical and numerical summaries of variables (demographics, lab measurements, vitals) in the ICU cohort.
